Solution-aware vs global ReLU ranking: \\ partial MILP strikes back for DNN verification

### 2025-01-25 CAV 2025 TODO/Paper_noProof.tex
update
Add a section
intro

\usepackage{hyperref}
\usepackage{url}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}

%\usepackage[latin9]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx}
\captionsetup{compatibility=false}
% \usepackage{esint}
\usepackage{array}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{url}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}

@@

\title{Hybrid MILP to efficiently and accuratly \\  solve hard DNN verification instances}
\date{}

@@

	\begin{abstract}
		$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
		trade-off between accuracy and runtime. VNNcomp however is focusing on relatively easy verification instances. In this paper, we consider {\em harder} verification instances, on which $\alpha,\beta$-Crown displays a large number ($20-58\%$) of undecided instances, that is, instances that can neither be verified, nor an explicit attack can be found. Enabling larger time-outs for $\alpha,\beta$-Crown only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time. Resorting to slow complete verifiers, does not fare better even with very large time-outs: They would theoretically be able to close the gap, but with an untractable runtime on all but small {\em hard} instances.

		In this paper, {\color{blue}
			%we study the MILP encoding of ReLU-DNNs.
			%, and provide new insights in the LP relaxation. 
			we propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
			the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input. }
		%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. 
		Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy. Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crown fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
	\end{abstract}

>>>>

\usepackage{hyperref}
\usepackage{url}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}
%\usepackage[latin9]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx}
\captionsetup{compatibility=false}
% \usepackage{esint}
\usepackage{array}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{url}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}

@@

\title{Solution-aware vs global ReLU ranking: \\
partial MILP strikes back for DNN verification}
\date{}

@@

	\begin{abstract}
		$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), 
		as the DNN verifier with the best trade-off between accuracy and runtime. 
		VNNcomp however is focusing on relatively easy verification problems.
		There are many problems however which are much harder to verify, and for which
		$\alpha,\beta$-Crown does not scale, even by enlarging tremendously the time-outs.
		Other techniques do not scale either.

		In this paper, we work on a fundamental problem to enable scaling to more complex problems:

		propose a novel Utility function that selects few neurons to be encoded with accurate but costly integer variables in a {\em partial MILP} problem. The novelty resides in the use of 
		the solution of {\em one} (efficient LP) solver to accurately compute a selection $\varepsilon$-optimal for a given input.
		%This allows us to carefully craft a {\em partial MILP} solution which selects automatically few neurons encoded as integer variables, the rest using the LP relaxation. 
		Compared with previous attempts, we can reduce the number of integer variables by around 4 times while maintaining the same level of accuracy. Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP for those for which $\alpha,\beta$-Crown fails, produces a very accurate yet efficient verifier, reducing tremendously the number of undecided instances ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance).
	\end{abstract}
